%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant IT Development Manager} % Job title
    {Hang Seng Indexes} % Organization
    {Mar 2023 - Present} % Location
    {} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Assistant Data Manager} % Job title
    {Hang Seng Indexes} % Organization
    {Dec 2021 - Mar 2023} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led Business Database Project, designed data operation flow to load figures of business products like ETP and F\&O to GCP BigQuery.}
        \item {Implemented unique identifiers in the database to map company identifiers from different market data vendors.}
        \item {Developed and shared common Python modules to make HTTP requests and connect to the database using the proxy required by the HSBC network. Established coding standards and rules across the team.}
        \item {Managed a team in designing Tableau "seed" reports and provided training to business teams to encourage the use of BI tools.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Analyst Programmer} % Job title
    {Hong Kong Monetary Authority} % Organization
    {Nov 2020 - Dec 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated 50 reports ETLs of economic and financial data, saving economists time from manual, repetitive tasks.}
        \item {Built Python scripts for data extraction, transformation, and analysis through web scraping and APIs.}
        \item {Designed dashboards to support economists in their economic and financial research, including the most viewed "Financial Market" dashboard.}
        \item {Refactored some dashboards to improve performance, leading to faster load time.}
        \item {Served as a scrum master in an agile project team, managing multiple project cycles from gathering business requirements to product backlog prioritization, effort estimation, and monitoring project progress.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {Agility Logistics} % Organization
    {Jan 2020 - Nov 2020} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained a "Sales Forecast vs Actual Variance" dashboard with the sales team to compare sales forecast to actual sales from the CRM system and track sales performance.}
        \item {Automated regular KPI reports using VBA macros.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
